Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

Their scarcity on the Sun has prompted efforts to create automated
oscillation detection algorithms.  The need for an automated
oscillation detection algorithm is also exacerbated by the large and
rapidly growing amount of AIA data, which means that the amount of
data that has to be searched is large.  There have been several
attempts at designing such algorithms.  \cite{2004SoPh..223....1D}
describe the design of an automated oscillation-detection algorithm
based on the wavelet analysis. The algorithm finds significant wave
packets ranging from single to multiple wave cycles in duration, by a
wavelet power/confidence level comparison against the null hypothesis
that a given time series is Gaussian-distributed noise.  Pixels with
significant oscillatory content are grouped manually.
\cite{2007SoPh..241..397N} take a similar approach, using a
thresholded fast Fourier transform to find locations in TRACE data
that may support an oscillatory signal. The threshold level is defined
as three to four times the average FFT power; if the maximum FFT power
is above this level then the frequency at which that power occurs is
assumed to be real.  \cite{2010SoPh..264..403I} assume that an
oscillatory signal is present in each location in the datacube and then
use a Bayesian-based treatment to calculate the probability that the
frequency has a particular value.  This algorithm relies on
subtracting a background trend from the time-series being tested, and
assumes that the noise is Gaussian distributed.

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193} for the corresponding AIA 171\AA\ plots.)}
\label{fig:dist171}
\end{figure}

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see
  also Figure \ref{fig:dist171} for the corresponding AIA
  171\AA\ plots.)}
\label{fig:dist193}
\end{figure}
Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
of the logarithm of the Fourier power for a small number of
frequencies, for all the pixels in each region.  The distributions all
follow a normal distribution approximately.  This indicates that the
power in each each at each frequency is approximately log-normally
distributed.  This observation guides the choice of how to average the
\PS\ over each of the selected region.  Since the Fourier
power is log-normally distributed, the arithmetic mean of the Fourier
power is biased by the very largest powers.  Since the logarithm of
the Fourier power is approximately Gaussian-distributed, the mean
value is a better representation of the range of values in the data.
Hence the mean of the logarithm of the Fourier power is used to
describe the mean \Fps\ of each region (note that
this is also equivalent to the geometric mean of the Fourier power.)

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\caption{Geometric mean of the Fourier power spectra in each of the
  four regions studied in AIA 171\AA\ (shown in black).  Also shown
  are the posterior mean and maximum likelihood fits for model $M_{1}$
  and $M_{2}$ (see Section \ref{sec:anal} and Appendix
  \ref{sec:app:ind} for more detail).  Model fit parameter values and
  their 68\% credible intervals are quoted in Table
  \ref{tab:parameters}. See also Figure \ref{fig:fit193} for the
  corresponding AIA 193\AA\ plots.}
\label{fig:fit171}
\end{figure}

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
\caption{Geometric mean of the Fourier power spectra in each of the
  four regions studied in AIA 193\AA\ (shown in black).  Also shown
  are the posterior mean and maximum likelihood fits for model $M_{1}$
  and $M_{2}$ (see Section \ref{sec:anal} and Appendix
  \ref{sec:app:ind} for more detail).  Model fit parameter values and
  their 68\% credible intervals are quoted in Table
  \ref{tab:parameters}. See also Figure \ref{fig:fit171} for the
  corresponding AIA 171\AA\ plots.}
\label{fig:fit193}
\end{figure}

>>>>

Their scarcity on the Sun has prompted efforts to create automated
oscillation detection algorithms.  The need for an automated
oscillation detection algorithm is also exacerbated by the large and
rapidly growing amount of AIA data, which means that the amount of
data that has to be searched is large.  There have been several
attempts at designing such algorithms, all of which operate on
time-series of two-dimensional image data (data cubes).
\cite{2004SoPh..223....1D} describe the design of an automated
oscillation-detection algorithm based on the wavelet analysis. The
algorithm finds significant wave packets ranging from single to
multiple wave cycles in duration, by a wavelet power/confidence level
comparison against the null hypothesis that a given time series is
Gaussian-distributed noise.  Pixels with significant oscillatory
content are grouped manually.  \cite{2007SoPh..241..397N} take a
similar approach, using a thresholded fast Fourier transform to find
locations in TRACE data that may support an oscillatory signal. The
threshold level is defined as three to four times the average FFT
power; if the maximum FFT power is above this level then the frequency
at which that power occurs is assumed to be real.
\cite{2010SoPh..264..403I} assume that an oscillatory signal is
present in each location in the datacube and then use a Bayesian-based
treatment to calculate the probability that the frequency has a
particular value.  This algorithm relies on subtracting a background
trend from the time-series being tested, and assumes that the noise is
Gaussian distributed.

@@

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{Distribution of Fourier power at some sample frequencies as a
function of AIA waveband and location.}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} show the distributions of the logarithm of
the Fourier power for a small number of frequencies, for all the
pixels in each region.  The distributions all follow a normal
distribution approximately.  This indicates that the power in each
each at each frequency is approximately log-normally distributed.
This observation guides the choice of how to average the \PS\ over
each of the selected region.  Since the Fourier power is log-normally
distributed, the arithmetic mean of the Fourier power is biased by the
very largest powers.  Since the logarithm of the Fourier power is
approximately Gaussian-distributed, the mean value is a better
representation of the range of values in the data.  Hence the mean of
the logarithm of the Fourier power is used to describe the mean
\Fps\ of each region (note that this is also equivalent to the
geometric mean of the Fourier power.)

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the Fourier power spectra in each of the
  four regions studied in AIA 171\AA\ (left column) and AIA
  193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section
  \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
  Model fit parameter values and their 68\% credible intervals are
  quoted in Table \ref{tab:parameters}. See also Figure
  \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
\label{fig:fit171}
\end{figure}
